InteroceptionStudy_GPValidation

### 2021-09-01 IAPS_PREPROCESSING_2021_1.Rmd
1

unique(db_HR_bio2.3.1$tNo)
db_HR_bio2.3.1
db_HR_bio2.3.2<-select()
db_HR_bio_final<- select(db_HR_bio2.3.1, c(1,12))

@@

tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final, by = c('ssid', 'tNo'))

>>>>

unique(db_HR_bio2.3.1$tNo)
db_HR_bio2.3.1
# db_HR_bio2.3.2<-select()
db_HR_bio_final<- select(db_HR_bio2.3.1, c(1:12))

@@

unique(tmp.df4_sum_full_bio$tNo)
tmp.df4_sum_full_bio$tNo3<- tmp.df4_sum_full_bio$tNo
tmp.df4_sum_full_bio1<- tmp.df4_sum_full_bio
tmp.df4_sum_full_bio1$tNo<-NULL

unique(tmp.df4_sum_full_bio$screencontent)
unique(db_HR_bio_final$screen_content)

tmp.df4_sum_full_bio$screen_content<- if_else(tmp.df4_sum_full_bio$screencontent == "ValenceResp", "valence",
                                              if_else(tmp.df4_sum_full_bio$screencontent == "IntResp", "arousal", tmp.df4_sum_full_bio$screencontent))

tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final, by = c('ssid', 'tNo', 'screen_content'))

unique(tmp.df4_sum_full_bio_hr$tNo)
